03-modeling

### 2018-05-07 02_scripts/031-laukiz1/03-modeling_laukiz1.Rmd
07/05/18

set.seed(12345)
resa_glmnet <- mlr::resample(tune_wrapper, task,
                             resampling = outer, extract = getTuneResult,
                             show.info = TRUE, measures = list(rmse))
parallelStop()
saveRDS(resa_glmnet, "/data/patrick/mod/hyperspectral/spcv/laukiz1_ridge.rda")
```

@@

```{r}
configureMlr(on.learner.error = "warn", on.error.dump = TRUE)
library(parallelMap)
parallelStart(mode = "multicore", level = "mlr.tuneParams", cpus = 40,
              mc.set.seed = TRUE) # only parallelize the tuning
set.seed(12345)
params_tuned_glmnet = tuneParams(lrn_glmnet, task = task, resampling = inner,
                                 par.set = ps_glmnet, control = ctrl, 
                                 measure = list(rmse))
parallelStop()
saveRDS("/data/patrick/mod/tmp/tuning_hyperspectral/tuning_bf1_ridge.rda")
```

@@

```{r}
lrn_glmnet_tuned <- makeLearner("regr.glmnet",
                                alpha = 0,
                                s = 1810,
                                standardize = FALSE, 
                                intercept = FALSE)

@@

@@

```{r}
ctrl <- makeTuneControlRandom(maxit = 200)
inner <- makeResampleDesc("SpCV", iters = 5)
```

@@

```{r}
outer <- makeResampleDesc("SpRepCV", folds = 5, reps = 2)
```

@@

parallelStop()
saveRDS(resa_glmnet, "/data/patrick/mod/hyperspectral/spcv/laukiz1_lasso.rda")
```

@@

parallelStop()
saveRDS(resa_glmnet, "/data/patrick/mod/hyperspectral/spcv/laukiz1_elasticnet")
```

>>>>

set.seed(12345)
resa_glmnet <- mlr::resample(tune_wrapper, task,
                             resampling = outer, extract = getTuneResult,
                             show.info = TRUE, measures = list(rmse))
parallelStop()
saveRDS(resa_glmnet, "/data/patrick/mod/hyperspectral/spcv/laukiz1_ridge_bf2_10folds.rda")
```

@@

```{r}
configureMlr(on.learner.error = "warn", on.error.dump = TRUE)
library(parallelMap)
parallelStart(mode = "multicore", level = "mlr.tuneParams", cpus = 48,
              mc.set.seed = TRUE) # only parallelize the tuning
set.seed(12345)
params_tuned_glmnet = tuneParams(lrn_glmnet, task = task, resampling = inner,
                                 par.set = ps_glmnet, control = ctrl, 
                                 measure = list(rmse))
parallelStop()
saveRDS(params_tuned_glmnet, "/data/patrick/mod/tmp/tuning_hyperspectral/tuning_bf2_ridge.rda")
```

@@

```{r}
lrn_glmnet_tuned <- makeLearner("regr.glmnet",
                                alpha = 0,
                                s = 7500,
                                standardize = FALSE, 
                                intercept = FALSE)

@@

```{r}
tibble(index = rownames(as.matrix(coef(glmnet_train_tuned$learner.model, s = 7610))), 
       coef = as.vector(as.matrix(coef(glmnet_train_tuned$learner.model, s = 7610)))) %>% 
  arrange(desc(coef))
```

```{r}
tibble(index = rownames(as.matrix(coef(glmnet_train_tuned$learner.model, s = 7610))), 
       coef = as.vector(as.matrix(coef(glmnet_train_tuned$learner.model, s = 7610)))) %>% 
  arrange(coef)
```

@@

@@

@@

parallelStop()
saveRDS(resa_glmnet, "/data/patrick/mod/hyperspectral/spcv/laukiz1_lasso_bf2_10folds.rda")
```

@@

parallelStop()
saveRDS(resa_glmnet, "/data/patrick/mod/hyperspectral/spcv/laukiz1_elasticnet_bf2_10folds.rda")
```

### 2018-05-07 02_scripts/032-laukiz2/03-modeling_laukiz2.Rmd
07/05/18

```{r}
task = makeRegrTask(id = "laukiz1", data = data, 
                    target = "deftot", coordinates = coords)
```

@@

```{r}
ps_glmnet <- makeParamSet(makeNumericParam("s", lower = 77, upper = 7700))
```

@@

set.seed(12345)
resa_glmnet <- mlr::resample(tune_wrapper, task,
                             resampling = outer, extract = getTuneResult,
                             show.info = TRUE, measures = list(rmse))
parallelStop()
saveRDS(resa_glmnet, "/data/patrick/mod/hyperspectral/spcv/laukiz1_ridge.rda")
```

@@

```{r}
configureMlr(on.learner.error = "warn", on.error.dump = TRUE)
library(parallelMap)
parallelStart(mode = "multicore", level = "mlr.tuneParams", cpus = 40,
              mc.set.seed = TRUE) # only parallelize the tuning
set.seed(12345)
params_tuned_glmnet = tuneParams(lrn_glmnet, task = task, resampling = inner,
                                 par.set = ps_glmnet, control = ctrl, 
                                 measure = list(rmse))
parallelStop()
saveRDS("/data/patrick/mod/tmp/tuning_hyperspectral/tuning_bf1_ridge.rda")
```

@@

```{r}
ps_glmnet <- makeParamSet(makeNumericParam("s", lower = 0.07, upper = 7.7))
```

```{r}
ctrl <- makeTuneControlRandom(maxit = 200)
inner <- makeResampleDesc("SpCV", iters = 5)
```

@@

parallelStop()
saveRDS(resa_glmnet, "/data/patrick/mod/hyperspectral/spcv/laukiz1_lasso.rda")
```

@@

```{r}
ps_glmnet <- makeParamSet(makeNumericParam("s", lower = 0.07, upper = 7700),
                          makeNumericParam("alpha", lower = 0, upper = 1))
```

@@

parallelStop()
saveRDS(resa_glmnet, "/data/patrick/mod/hyperspectral/spcv/laukiz1_elasticnet")
```

>>>>

```{r}
task = makeRegrTask(id = "laukiz2", data = data, 
                    target = "deftot", coordinates = coords)
```

@@

```{r}
ps_glmnet <- makeParamSet(makeNumericParam("s", lower = 102, upper = 10228))
```

@@

set.seed(12345)
resa_glmnet <- mlr::resample(tune_wrapper, task,
                             resampling = outer, extract = getTuneResult,
                             show.info = TRUE, measures = list(rmse))
parallelStop()
saveRDS(resa_glmnet, "/data/patrick/mod/hyperspectral/spcv/laukiz2_ridge_bf2_10folds.rda")
```

@@

```{r}
configureMlr(on.learner.error = "warn", on.error.dump = TRUE)
library(parallelMap)
parallelStart(mode = "multicore", level = "mlr.tuneParams", cpus = 48,
              mc.set.seed = TRUE) # only parallelize the tuning
set.seed(12345)
params_tuned_glmnet = tuneParams(lrn_glmnet, task = task, resampling = inner,
                                 par.set = ps_glmnet, control = ctrl, 
                                 show.info = TRUE, measure = list(rmse))
parallelStop()
saveRDS(params_tuned_glmnet, "/data/patrick/mod/tmp/tuning_hyperspectral/tuning_bf2_ridge.rda")
```

@@

```{r}
ps_glmnet <- makeParamSet(makeNumericParam("s", lower = 0.1, upper = 10.2))
```

@@

parallelStop()
saveRDS(resa_glmnet, "/data/patrick/mod/hyperspectral/spcv/laukiz2_lasso_bf2_10folds.rda")
```

@@

```{r}
ps_glmnet <- makeParamSet(makeNumericParam("s", lower = 0.1, upper = 10228),
                          makeNumericParam("alpha", lower = 0, upper = 1))
```

@@

parallelStop()
saveRDS(resa_glmnet, "/data/patrick/mod/hyperspectral/spcv/laukiz2_elasticnet.rda")
```

### 2018-05-07 02_scripts/033-luiando/03-modeling_luiando.Rmd
26/04/18
07/05/18

```{r}
data = data[[2]]
coords = coords[[2]]
```

@@

```{r}
task = makeRegrTask(id = "laukiz1", data = data, 
                    target = "deftot", coordinates = coords)
```

@@

```{r}
# predict.type for 'auc' (AUROC)
lrn_glmnet <- makeLearner("regr.glmnet",
                          alpha = 0,
                          standardize = FALSE)
                          #lambda = sort(seq(0, 5, length.out = 100), decreasing = T))
getHyperPars(lrn_glmnet)
getParamSet(lrn_glmnet)
```

@@

```{r}
ps_glmnet <- makeParamSet(makeNumericParam("s", lower = 30, upper = 3300))
```

```{r}
ctrl <- makeTuneControlRandom(maxit = 500)
inner <- makeResampleDesc("SpCV", iters = 5)
```

```{r}
configureMlr(on.learner.error = "warn", on.error.dump = TRUE)
library(parallelMap)
parallelStart(mode = "multicore", level = "mlr.tuneParams", cpus = 40,
              mc.set.seed = TRUE) # only parallelize the tuning
set.seed(12345)
params_tuned_glmnet = tuneParams(lrn_glmnet, task = task, resampling = inner,
                                 par.set = ps_glmnet, control = ctrl, 
                                 measure = list(rmse))
parallelStop()
saveRDS("/data/patrick/mod/tmp/tuning_hyperspectral/tuning_bf1_ridge.rda")
```

@@

set.seed(12345)
resa_glmnet <- mlr::resample(tune_wrapper, task,
                             resampling = outer, extract = getTuneResult,
                             show.info = TRUE, measures = list(rmse))
parallelStop()
saveRDS(resa_glmnet, "/data/patrick/mod/hyperspectral/spcv/laukiz1_ridge.rda")
```

@@

```{r}
ps_glmnet <- makeParamSet(makeNumericParam("s", lower = 0.03, upper = 3.3))
```

```{r}
ctrl <- makeTuneControlRandom(maxit = 500)
inner <- makeResampleDesc("SpCV", iters = 5)
```

@@

@@

parallelStop()
saveRDS(resa_glmnet, "/data/patrick/mod/hyperspectral/spcv/laukiz1_lasso.rda")
```

@@

For the elasticnet we also tune `alpha`.

```{r}
ps_glmnet <- makeParamSet(makeNumericParam("s", lower = 0.03, upper = 3.3),
                          makeNumericParam("alpha", lower = 0, upper = 1))
```

```{r}
ctrl <- makeTuneControlRandom(maxit = 200)
inner <- makeResampleDesc("SpCV", iters = 5)
```

@@

parallelStop()
saveRDS(resa_glmnet, "/data/patrick/mod/hyperspectral/spcv/laukiz1_elasticnet")
```

>>>>

```{r}
data = data[[3]]
coords = coords[[3]]
```

@@

```{r}
task = makeRegrTask(id = "luiando", data = data, 
                    target = "deftot", coordinates = coords)
```

@@

```{r}
# predict.type for 'auc' (AUROC)
lrn_glmnet <- makeLearner("regr.glmnet",
                          alpha = 0,
                          standardize = FALSE,
                          intercept = FALSE)
                          #lambda = sort(seq(0, 5, length.out = 100), decreasing = T))
# getHyperPars(lrn_glmnet)
# getParamSet(lrn_glmnet)
```

@@

```{r}
ps_glmnet <- makeParamSet(makeNumericParam("s", lower = 15, upper = 1560))
```

```{r}
ctrl <- makeTuneControlRandom(maxit = 200)
inner <- makeResampleDesc("SpCV", iters = 10)
```

@@

set.seed(12345)
resa_glmnet <- mlr::resample(tune_wrapper, task,
                             resampling = outer, extract = getTuneResult,
                             show.info = TRUE, measures = list(rmse))
parallelStop()
saveRDS(resa_glmnet, "/data/patrick/mod/hyperspectral/spcv/all_plots_ridge_bf2_10folds.rda")
```

```{r}
configureMlr(on.learner.error = "warn", on.error.dump = TRUE)
library(parallelMap)
parallelStart(mode = "multicore", level = "mlr.tuneParams", cpus = 48,
              mc.set.seed = TRUE) # only parallelize the tuning
set.seed(12345)
params_tuned_glmnet = tuneParams(lrn_glmnet, task = task, resampling = inner,
                                 par.set = ps_glmnet, control = ctrl, 
                                 show.info = TRUE, measure = list(rmse))
parallelStop()
saveRDS(params_tuned_glmnet, "/data/patrick/mod/tmp/tuning_hyperspectral/tuning_bf2_ridge.rda")
```

@@

```{r}
ps_glmnet <- makeParamSet(makeNumericParam("s", lower = 0.01, upper = 1.56))
```

```{r}
ctrl <- makeTuneControlRandom(maxit = 200)
inner <- makeResampleDesc("SpCV", iters = 10)
```

@@

```{r}
library(parallelMap)
parallelStart(mode = "multicore", level = "mlr.tuneParams", cpus = 48,
              mc.set.seed = TRUE) # only parallelize the tuning

@@

parallelStop()
saveRDS(resa_glmnet, "/data/patrick/mod/hyperspectral/spcv/luiando_lasso_bf2_10folds.rda")
```

@@

For the elasticnet we also tune `alpha`.
As we have both penalties, we just use the lower and uppper maxima from both Lasso and Ridge.

```{r}
ps_glmnet <- makeParamSet(makeNumericParam("s", lower = 0.01, upper = 1560),
                          makeNumericParam("alpha", lower = 0, upper = 1))
```

```{r}
ctrl <- makeTuneControlRandom(maxit = 200)
inner <- makeResampleDesc("SpCV", iters = 10)
```

@@

parallelStop()
saveRDS(resa_glmnet, "/data/patrick/mod/hyperspectral/spcv/luiando_elasticnet.rda")
```

```{r}
configureMlr(on.learner.error = "warn", on.error.dump = TRUE)
library(parallelMap)
parallelStart(mode = "multicore", level = "mlr.tuneParams", cpus = 48,
              mc.set.seed = TRUE) # only parallelize the tuning
set.seed(12345)
params_tuned_glmnet = tuneParams(lrn_glmnet, task = task, resampling = inner,
                                 par.set = ps_glmnet, control = ctrl, 
                                 measure = list(rmse))
parallelStop()
```

### 2018-05-07 02_scripts/034-oiartzun/03-modeling_oiartzun.Rmd
07/05/18

Lauki1: 7594
Laukiz2: 7594
Oiartzun: 7891
Luiando: 6073

@@

```{r}
data = data[[3]]
coords = coords[[3]]
```

@@

```{r}
task = makeRegrTask(id = "luiando", data = data, 
                    target = "deftot", coordinates = coords)
```

@@

```{r}
ps_glmnet <- makeParamSet(makeNumericParam("s", lower = 15, upper = 1560))
```

@@

set.seed(12345)
resa_glmnet <- mlr::resample(tune_wrapper, task,
                             resampling = outer, extract = getTuneResult,
                             show.info = TRUE, measures = list(rmse))
parallelStop()
saveRDS(resa_glmnet, "/data/patrick/mod/hyperspectral/spcv/all_plots_ridge_bf2_10folds.rda")
```

@@

```{r}
ps_glmnet <- makeParamSet(makeNumericParam("s", lower = 0.01, upper = 1.56))
```

@@

parallelStop()
saveRDS(resa_glmnet, "/data/patrick/mod/hyperspectral/spcv/luiando_lasso_bf2_10folds.rda")
```

@@

```{r}
ps_glmnet <- makeParamSet(makeNumericParam("s", lower = 0.01, upper = 1560),
                          makeNumericParam("alpha", lower = 0, upper = 1))
```

@@

parallelStop()
saveRDS(resa_glmnet, "/data/patrick/mod/hyperspectral/spcv/luiando_elasticnet.rda")
```

>>>>

Lauki1: 7594
Laukiz2: 7594
Oiartzun: 7891
oiartzun: 6073

@@

```{r}
data = data[[4]]
coords = coords[[4]]
```

@@

```{r}
task = makeRegrTask(id = "oiartzun", data = data, 
                    target = "deftot", coordinates = coords)
```

@@

```{r}
ps_glmnet <- makeParamSet(makeNumericParam("s", lower = 55, upper = 5525))
```

@@

set.seed(12345)
resa_glmnet <- mlr::resample(tune_wrapper, task,
                             resampling = outer, extract = getTuneResult,
                             show.info = TRUE, measures = list(rmse))
parallelStop()
saveRDS(resa_glmnet, "/data/patrick/mod/hyperspectral/spcv/oiartzun_ridge_bf2_10folds.rda")
```

@@

```{r}
ps_glmnet <- makeParamSet(makeNumericParam("s", lower = 0.05, upper = 5.5))
```

@@

parallelStop()
saveRDS(resa_glmnet, "/data/patrick/mod/hyperspectral/spcv/oiartzun_lasso_bf2_10folds.rda")
```

@@

```{r}
ps_glmnet <- makeParamSet(makeNumericParam("s", lower = 0.05, upper = 5525),
                          makeNumericParam("alpha", lower = 0, upper = 1))
```

@@

parallelStop()
saveRDS(resa_glmnet, "/data/patrick/mod/hyperspectral/spcv/oiartzun_elasticnet.rda")
```

### 2018-05-07 02_scripts/035_all-plots/03-modeling_all.Rmd
07/05/18

```{r, results='hide'}
library(mlr)
library(glue)
library(sf)
library(dplyr)
library(tibble)
library(purrr)
library(magrittr)
library(data.table)
library(pbmcapply)
```

@@

Lauki1: 7594
Laukiz2: 7594
Oiartzun: 7891
Luiando: 6073

@@

# Select plot

```{r}
data = data[[1]]
coords = coords[[1]]
```

@@

```{r}
task = makeRegrTask(id = "laukiz1", data = data, 
                    target = "deftot", coordinates = coords)
```

@@

```{r}
ps_glmnet <- makeParamSet(makeNumericParam("s", lower = 30, upper = 3300))
```

```{r}
ctrl <- makeTuneControlRandom(maxit = 500)
inner <- makeResampleDesc("SpCV", iters = 5)
```

```{r}
configureMlr(on.learner.error = "warn", on.error.dump = TRUE)
library(parallelMap)
parallelStart(mode = "multicore", level = "mlr.tuneParams", cpus = 40,
              mc.set.seed = TRUE) # only parallelize the tuning
set.seed(12345)
params_tuned_glmnet = tuneParams(lrn_glmnet, task = task, resampling = inner,
                                 par.set = ps_glmnet, control = ctrl, 
                                 measure = list(rmse))
parallelStop()
saveRDS("/data/patrick/mod/tmp/tuning_hyperspectral/tuning_bf1_ridge.rda")
```

@@

```{r}
outer <- makeResampleDesc("SpRepCV", folds = 10, reps = 2)
```

@@

set.seed(12345)
resa_glmnet <- mlr::resample(tune_wrapper, task,
                             resampling = outer, extract = getTuneResult,
                             show.info = TRUE, measures = list(rmse))
parallelStop()
saveRDS(resa_glmnet, "/data/patrick/mod/hyperspectral/spcv/laukiz1_ridge.rda")
```

@@

```{r}
ps_glmnet <- makeParamSet(makeNumericParam("s", lower = 0.03, upper = 3.3))
```

```{r}
ctrl <- makeTuneControlRandom(maxit = 500)
inner <- makeResampleDesc("SpCV", iters = 5)
```

@@

```{r}
outer <- makeResampleDesc("SpRepCV", folds = 10, reps = 2)
```

parallelStop()
saveRDS(resa_glmnet, "/data/patrick/mod/hyperspectral/spcv/laukiz1_lasso.rda")
```

@@

For the elasticnet we also tune `alpha`.

```{r}
ps_glmnet <- makeParamSet(makeNumericParam("s", lower = 0.03, upper = 3.3),
                          makeNumericParam("alpha", lower = 0, upper = 1))
```

```{r}
ctrl <- makeTuneControlRandom(maxit = 200)
inner <- makeResampleDesc("SpCV", iters = 5)
```

@@

```{r}
outer <- makeResampleDesc("SpRepCV", folds = 10, reps = 2)
```

@@

parallelStop()
saveRDS(resa_glmnet, "/data/patrick/mod/hyperspectral/spcv/laukiz1_elasticnet")
```

>>>>

```{r, results='hide'}
devtools::install_github("tidyverse/ggplot2")
devtools::install_github("pat-s/mlr@blocking_visualization")

library(mlr)
library(glue)
library(sf)
library(dplyr)
library(tibble)
library(purrr)
library(magrittr)
library(data.table)
library(pbmcapply)
```

@@

Lauki1: 7594
Laukiz2: 7594
Oiartzun: 7841
Luiando: 7471

@@

# Merge into one dataset

Leaving out Luiando (see README for reason).

```{r}
data = as_tibble(rbindlist(data, fill = TRUE))
data = Filter(function(x) !any(is.na(x)), data)
coords = as_tibble(rbindlist(coords))
```

@@

```{r}
task = makeRegrTask(id = "all_plots", data = data, 
                    target = "deftot", coordinates = coords,
                    blocking = factor(rep(1:4, c(559, 382, 301, 499))))
```

@@

```{r}
ps_glmnet <- makeParamSet(makeNumericParam("s", lower = 35, upper = 3559))
```

```{r}
ctrl <- makeTuneControlRandom(maxit = 200)
inner <- makeResampleDesc("CV", iters = 3)
```

@@

```{r}
outer <- makeResampleDesc("RepCV", folds = 4, reps = 2)
outer <- makeResampleDesc("Blocking")
```

@@

set.seed(12345)
resa_glmnet <- mlr::resample(tune_wrapper, task,
                             resampling = outer, extract = getTuneResult,
                             show.info = TRUE, measures = list(rmse))
parallelStop()
saveRDS(resa_glmnet, "/data/patrick/mod/hyperspectral/spcv/all_plots_ridge_bf2_10folds.rda")
```

#### Visualize partitions

```{r}
resa_glmnet= readRDS("/data/patrick/mod/hyperspectral/spcv/all_plots_ridge_bf2_10folds.rda")
plot = createSpatialResamplingPlots(task, list("Blocking" = resa_glmnet), crs = 32630)
cowplot::plot_grid(plotlist = plot[["Plots"]], ncol = 4, nrow = 1, labels = plot[["Labels"]])
```

```{r}
configureMlr(on.learner.error = "warn", on.error.dump = TRUE)
library(parallelMap)
parallelStart(mode = "multicore", level = "mlr.tuneParams", cpus = 48,
              mc.set.seed = TRUE) # only parallelize the tuning
set.seed(12345)
params_tuned_glmnet = tuneParams(lrn_glmnet, task = task, resampling = inner,
                                 par.set = ps_glmnet, control = ctrl, 
                                 show.info = TRUE, measure = list(rmse))
parallelStop()
saveRDS(params_tuned_glmnet, "/data/patrick/mod/tmp/tuning_hyperspectral/tuning_bf2_ridge.rda")
```

@@

```{r}
ps_glmnet <- makeParamSet(makeNumericParam("s", lower = 0.03, upper = 3.5))
```

```{r}
ctrl <- makeTuneControlRandom(maxit = 200)
inner <- makeResampleDesc("SpCV", iters = 10)
```

```{r}
outer <- makeResampleDesc("Blocking")
```

```{r}
library(parallelMap)
parallelStart(mode = "multicore", level = "mlr.tuneParams", cpus = 48,
              mc.set.seed = TRUE) # only parallelize the tuning

parallelStop()
saveRDS(resa_glmnet, "/data/patrick/mod/hyperspectral/spcv/all_plots_lasso_bf2_10folds.rda")
```

@@

@@

For the elasticnet we also tune `alpha`.
As we have both penalties, we just use the lower and uppper maxima from both Lasso and Ridge.

```{r}
ps_glmnet <- makeParamSet(makeNumericParam("s", lower = 0.03, upper = 3559),
                          makeNumericParam("alpha", lower = 0, upper = 1))
```

```{r}
ctrl <- makeTuneControlRandom(maxit = 200)
inner <- makeResampleDesc("SpCV", iters = 10)
```

@@

```{r}
outer <- makeResampleDesc("Blocking")
```

@@

parallelStop()
saveRDS(resa_glmnet, "/data/patrick/mod/hyperspectral/spcv/all_plots_elasticnet.rda")
```

```{r}
configureMlr(on.learner.error = "warn", on.error.dump = TRUE)
library(parallelMap)
parallelStart(mode = "multicore", level = "mlr.tuneParams", cpus = 48,
              mc.set.seed = TRUE) # only parallelize the tuning
set.seed(12345)
params_tuned_glmnet = tuneParams(lrn_glmnet, task = task, resampling = inner,
                                 par.set = ps_glmnet, control = ctrl, 
                                 measure = list(rmse))
parallelStop()
```
